% Acknowledgments.tex

\begin{acknowledgments}

First and foremost, I express my deep gratitude to my supervisor Professor Takayuki OKATANI for the immense support and illuminating guidance. Truly, without his guidance and unwavering will to share knowledge, this work would not be possible in the state that it is now. I am forever grateful for having the opportunity to work under his supervision.

"I would like to express my heartfelt gratitude to Professor Hiroyuki TAKIZAWA and Associate Professor Shingo KAGAMI for their exceptional guidance and support as members of my thesis committee. Their time, insightful feedback, and unwavering encouragement have been immensely valuable throughout this journey."

I am sincerely grateful to Assistant Professor Masanori SUGANUMA for the guidance and encouragement during times of uncertainty an overall my research.

I would like to share my thankfulness to the members of the Computer Vision lab, namely Kang Jun LIU, Nguyen Van QUANG, Bonappol LIMANOND, Kitto?? for the support and experience they shared with me throughout my research. 

I also extend my appreciation for my family members, my parents BOBOJANOVA U. and BOLTABOYEV Sh. for their tremendous support throughout my life, without them I would not be here to write this work. I am also grateful to my sister RAKHIMOVA M. for always being encouraging and inspiring in all she does.

I am deeply appreciative of all the individuals mentioned above, along with everyone who, through various means, both directly and indirectly, have aided me in the completion of this work.

\end{acknowledgments}